---
title: "Grey Literature Search on Multiple Websites with rkagi"
author: "Rainer Krug"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: show
    df-print: paged
vignette: >
  %\VignetteIndexEntry{Grey Literature Search using rkagi}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
execute:
  echo: true
  warning: false
  message: false
---
# Setup

```{r}
#| label: setup

# devtools::load_all()
library(rkagi)
library(here)

# Paths: read via system.file(); write via here::here() into inst/extdata
shipped_extdata <- function(filename) system.file("extdata", filename, package = "rkagi")
write_extdata   <- function(filename) here::here("inst", "extdata", filename)
```

# Methods

## Define Connection Object


```{r}
#| label: define-connection-object

conn <- new_kagi_connection(
  endpoint = "search",
  api_key = function() {
    keyring::key_get("API_kagi")
  }
)
```
## Search

### Define Search Objects

```{r}
#| label: define-search-objects

domains <- c(
  "worldbank.org",
  "fao.org",
  "ipbes.net",
  "arxiv.org",
  "researchgate.net",
  "biorxiv.org",
  "osf.io",
  "zenodo.org"
)

query <- "biodiversity"

queries <- build_kagi_query(
  q = query,
  filetype = c("pdf", "docx"),
  site = domains,
  inurl = NULL,
  intitle = NULL
)

searches <- lapply(
  queries,
  function(q) {
    new_kagi_search(
      conn,
      q,
      limit = 100
    )
  }
)

```

### Perform Searches

```{r}
#| label: perform-search

read_path <- shipped_extdata("search_results.rds")
if (!(nzchar(read_path) && file.exists(read_path))) {
  search_results <- lapply(
    searches,
    function(s) {
      message("Performing search for query: ", s$q)
      res <- kagi_perform(s)
      message("    Search completed with ", res$data |> nrow(), " hits.")
      return(res)
    }
  )

  # Create directory if it doesn't exist
  write_path <- write_extdata("search_results.rds")
  dir.create(dirname(write_path), recursive = TRUE, showWarnings = FALSE)

  # Save results
  saveRDS(search_results, write_path)
} else {
  message(
    "Loading existing search results from ", read_path
  )
  search_results <- readRDS(read_path)
}
```

### Combine Search Results

```{r}
#| label: combine-search-results

read_path <- shipped_extdata("search_result.rds")
if (!(nzchar(read_path) && file.exists(read_path))) {
  search_result <- dplyr::bind_rows(
    lapply(
      search_results,
      function(x) {
        x$data
      }
    )
  )

  # Create directory if it doesn't exist
  write_path <- write_extdata("search_result.rds")
  dir.create(dirname(write_path), recursive = TRUE, showWarnings = FALSE)

  # Save results
  saveRDS(search_result, write_path)
} else {
  message("Loading existing search results from ", read_path)
  search_result <- readRDS(read_path)
}
```

## Enrich 

### Define Enrich Objects

```{r}
#| label: define-enrich-objects

enrichments <- lapply(
  query,
  function(x) {
    new_kagi_enrich(
      conn = conn,
      q = x,
      limit = 100
    )
  }
)
```


### Perform Enrichment


```{r}
#| label: perform-enrichment

enrich_results <- lapply(
  enrichments,
  function(s) {
    message("Performing enrichment for query: ", s$q)
    res <- kagi_perform(s)
    message("    Enrichment completed with ", res$data |> nrow(), " hits.")
    return(res)
  }
)

```


### Combine Enrich Results

```{r}
#| label: combine-enrich-results

read_path <- shipped_extdata("enrich_results.rds")
if (!(nzchar(read_path) && file.exists(read_path))) {
  enrich_result <- dplyr::bind_rows(
    lapply(
      enrich_results,
      function(x) {
        x$data
      }
    )
  )

  # Create directory if it doesn't exist
  write_path <- write_extdata("enrich_results.rds")
  dir.create(dirname(write_path), recursive = TRUE, showWarnings = FALSE)

  # Save results
  saveRDS(enrich_result, write_path)
} else {
  message(
    "Loading existing enrich results from ", read_path
  )
  enrich_result <- readRDS(read_path)
}

```


## Summarize Search Results

### Define Summarize Objects for Search

```{r}
#| label: define-summarize-search-objects

search_summaries <- lapply(
  search_result$url,
  function(x) {
    new_kagi_summarize(
      conn = conn,
      url = x,
      text = NULL,
      engine = "cecil",
      summary_type = "summary",
      target_language = "EN"
    )
  }
)
```

### Perform Summarization of Search

```{r}
#| label: perform-search-summarization

read_path <- shipped_extdata("summary_search_results.rds")
if (!(nzchar(read_path) && file.exists(read_path))) {
  summarize_search_results <- lapply(
    search_summaries,
    function(s) {
      message("Performing summarization for url: ", s$url)
      res <- kagi_perform(s)
      message("    Summarization completed.")
      return(res)
    }
  )

  # Create directory if it doesn't exist
  write_path <- write_extdata("summary_search_results.rds")
  dir.create(dirname(write_path), recursive = TRUE, showWarnings = FALSE)

  # Save results
  saveRDS(summarize_search_results, write_path)
} else {
  message(
    "Loading existing summary search results from ", read_path
  )
  summarize_search_results <- readRDS(read_path)
}

```


## Summarize Enrich Results

### Define Summarize Objects for Enrich

```{r}
#| label: define-summarize-enrich-objects

enrich_summaries <- lapply(
  enrich_result$url,
  function(x) {
    new_kagi_summarize(
      conn = conn,
      url = x,
      text = NULL,
      engine = "cecil",
      summary_type = "summary",
      target_language = "EN"
    )
  }
)
```

### Perform Summarization of Enrichment

```{r}
#| label: perform-enrich-summarization


read_path <- shipped_extdata("summary_enrich_results.rds")
if (!(nzchar(read_path) && file.exists(read_path))) {
  summarize_enrich_results <- lapply(
    enrich_summaries,
    function(s) {
      message("Performing summarization for url: ", s$url)
      res <- kagi_perform(s)
      message("    Summarization completed.")
      return(res)
    }
  )

  # Create directory if it doesn't exist
  write_path <- write_extdata("summary_enrich_results.rds")
  dir.create(dirname(write_path), recursive = TRUE, showWarnings = FALSE)

  # Save results
  saveRDS(summarize_enrich_results, write_path)
} else {
  message(
    "Loading existing summary enrich results from ", read_path
  )
  summarize_enrich_results <- readRDS(read_path)
}

```


# Results

## Search Results

```{r}
#| label: search-results
readRDS(shipped_extdata("search_result.rds"))
```

## Enrich Results

```{r}
#| label: enrich-results

readRDS(shipped_extdata("enrich_results.rds"))
```
